\documentclass[11pt,letter,sans]{moderncv}

\moderncvstyle{banking}
\moderncvcolor{blue}

\usepackage[scale=0.81]{geometry}
\usepackage[none]{hyphenat}
\usepackage[utf8]{inputenc}
\usepackage[document]{ragged2e}

\nopagenumbers{}

\newcommand*{\cvsimple}[4][.25em]{
  \begin{tabular*}{\maincolumnwidth}{l@{\extracolsep{\fill}}r}
    {\itshape #3} & {\itshape #2}\\
  \end{tabular*}
  \ifx&#4&
  \else{\\
    \begin{minipage}{\maincolumnwidth}
      \small#4
    \end{minipage}}\fi
  \par\addvspace{#1}}

\name{Steven}{Heidel}
\phone[fixed]{+1~(650)~944~9541}
\email{steven@heidel.ca}
\homepage{stevenheidel.com}

\begin{document}

\makecvtitle

\vspace{-0.8cm}

\section{Experience}

\cventry{Oct 2019 -- Present}{Software Engineer (L6)}{Airbnb}{San Francisco, CA}{}{
\begin{itemize}
\item Managed a team of four software engineers in a hybrid manager / tech lead role.
\item Led migration to a new document storage system, deployed caching systems, and built materialized views with Kafka and Elasticsearch. This led to better performance and saved over \$1.5M a year.
\item Implemented a custom coroutine scheduler in Kotlin to improve performance and throughput of a service which handles 75\% of Airbnb's traffic.
\end{itemize}
}

\cventry{May 2018 -- May 2019}{Software Engineering Manager}{Rigetti Quantum Computing}{Berkeley, CA}{}{
\begin{itemize}
\item Managed a team of software engineers during a period of high growth, grew team from two to six.
\item Led software engineer hiring: set up hiring process, trained interviewers, and gave final sign off.
\item Author of specialized language for expressing pulse sequences used in automated device calibration.
\item Scaled Postgres to handle terabytes of experimental physics data. Consolidated all design, measurement, and fab data into a single database.
\item Delivered multiple wins including improving fabrication efficiency, greater visibility into quantum experiments, and orders of magnitude increases to performance.
\end{itemize}
}

\cvsimple{Sep 2017 -- May 2018}{Senior Software Engineer}{
\begin{itemize}
\item Led development of Rigetti's first cloud quantum computing product. Backend was implemented with Python 3 using asyncio, frontend was implemented with React, GraphQL, and Typescript.
\item Created a highly optimized open-source RPC framework over ZeroMQ.
\end{itemize}
}

\cventry{Dec 2016 -- Sep 2017}{Staff Software Engineer}{LinkedIn}{San Francisco, CA}{}{
\begin{itemize}
\item Lead engineer on the Enterprise Platform (EP) team. EP provides common functionality such as license management, external integrations, and access control to all enterprise applications at LinkedIn.
\item Rebuilt enterprise search platform from the ground up to use Elasticsearch. This increased maintainability, performance, and led to a 10x decrease in cost. Used Spark to build offline indexes.
\item Led team to migrate Sales Navigator from a legacy system to EP which enabled a 10 figure sales deal.
\item Gave company-wide engineering presentation on functional programming and composition in Java 8.
\end{itemize}
}

\cvsimple{Sep 2015 -- Dec 2016}{Senior Software Engineer}{
\begin{itemize}
\item Worked on LinkedIn Lookup: the fastest way to find, learn about, and contact anyone at your company.
\item Architected the API server using Scala and Play to communicate with the web and mobile apps.
\item Worked with growth and messaging teams to optimize member communications from actions generated by the app using Kafka and Samza for the data pipeline.
\item Maintainer of open source Scala library called Clump which automatically optimizes microservice calls, providing a powerful and composable interface for aggregating resources.
\end{itemize}
}

\cvsimple{Aug 2014 -- Sept 2015}{Software Engineer}{
\begin{itemize}
\item Worked on Campaign Manager: a product which advertisers use to manage \$400M worth of ads per year.
\item Added key features and refactored inefficient code to create a faster and better user experience.
\end{itemize}
}

\cventry{Mar 2013 -- Aug 2014}{Co-Founder and CTO}{Encore}{Toronto, ON}{}{
\begin{itemize}
\item Encore was an iPhone app designed around the memories created at live music shows.
\item Founded as part of The Next 36 startup accelerator program, which included both venture funding and a subset of MBA classes from the University of Toronto.
\end{itemize}
}

\section{Education}

\cventry{Sep 2009 -- Apr 2014}{B.Sc. (High Honours) in Computer Science, Minor in Mathematics}{University of Saskatchewan}{Saskatoon, SK}{}{}

\end{document}