\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{banking}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Steven}{Heidel}
\title{Cover Letter}                               % optional, remove / comment the line if not wanted
%\address{City}{Country}% optional, remove / comment the line if not wanted; the "postcode city" and "country" arguments can be omitted or provided empty
\phone[fixed]{+1~(306)~341~4778}                   % optional, remove / comment the line if not wanted; the optional "type" of the phone can be "mobile" (default), "fixed" or "fax"
%\phone[fixed]{+2~(345)~678~901}
%\phone[fax]{+3~(456)~789~012}
\email{steven@heidel.ca}                               % optional, remove / comment the line if not wanted
\homepage{www.stevenheidel.me}                         % optional, remove / comment the line if not wanted
\social[linkedin]{stevenheidel}                        % optional, remove / comment the line if not wanted
\social[twitter]{@stevenheidel}                             % optional, remove / comment the line if not wanted
\social[github]{stevenheidel}                              % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

\begin{document}

% recipient data
\recipient{Google}{}
\date{\today{}}
\opening{Dear Sir or Madam,}
\closing{Yours faithfully,}
\enclosure[Attached]{R\'esum\'e}
\makelettertitle

Hello,

I use Google products for almost everything because I know that they are built by teams of very diverse, intelligent, and creative people. I want to be one of those people. I will be graduating in April 2014 with an honours degree in Computer Science and a minor in mathematics. Please consider this as my application to join Google when I graduate.

During my time at the University of Saskatchewan, I have taught tutorials and study sessions to first year computer science students and have twice been asked by professors to join their research teams. In my spare time I have taught myself new technologies and completed various web/mobile development projects. I have even set up a personal web design company and have completed several websites for local businesses. I have also volunteered my time to a global open source software project.

As an office consultant at a Prince Albert occupational therapy clinic I completed various computer-related projects during the two summers I worked there. This included creating a custom application to manage their medical documents which decreased the amount of time needed to scan and upload new documents by fifty percent.

In 2010 I was selected to be part of Skills Canada in the WorldSkills trades competition. As a competitor in the "IT Solutions for Business" category I twice placed 1st at Nationals and placed 4th at the World Competition in London. Since then I’ve continued to be involved in Skills Canada to attract more students and sponsors to the program.

Last year I decided to try something new and ran for Vice President of the University of Saskatchewan Students’ Union. I was elected and have since gained such experience as working in an office team, managing time, public speaking, and decision making. 

Over the summer I participated in a program called "The Next 36" where we started a business and took courses from MBA professors at the U of T.

I believe that my studies, extracurricular activities, and past work experience have provided a strong background that will greatly benefit your team, as demonstrated on my resume. If you have any questions or require further information, feel free to contact me through my phone number or email address. Thank you for your time in considering my application. I look forward to hearing from you.

\makeletterclosing

\end{document}